---
title: "Mapping Goosies: <br> A Goose Journey"
author: "A. Mott & M. Kramer"
date: "Winter 2020"
logo: SNGO.jpg
output: ioslides_presentation
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library("jpeg")
```

## Packages Used

```{r echo=TRUE, message=FALSE, warning=FALSE}
library("devtools")
library("ggmap")
library("tidyverse")
library("rgeos")
library("rgdal")
library("naniar")
library("shiny")
library("shinydashboard")
```
```{r include=FALSE}
snow <- read_csv("Data/SNGO_Colville_180965.csv")
```

## Rocket Netting
<iframe width="560" height="315" src="https://www.youtube.com/embed/HPDa-YQHKRY" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>


## Molt Drive
<iframe width="560" height="315" src="https://www.youtube.com/embed/wqev8JY7Amk" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

## Goose Capture
<iframe width="560" height="315" src="https://www.youtube.com/embed/YrgeZwXEb5w" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

## Setting Parameters
```{r echo=TRUE, message=FALSE, warning=FALSE}
snow %>% 
  select(Latitude, Longitude) %>% 
  summary()
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
lat <- c(39.20, 70.49)
long <- c(-160.6, -110.2)
bbox <- make_bbox(long, lat, f = 0.05)
```

## Getting a Base Map


```{r echo=TRUE, message=FALSE, warning=FALSE}
b <- get_map(bbox, maptype = "terrain", source = "stamen")
ggmap(b)
```


## Adding Goose Location Points
- Solar powered transmitters collect GPS locations of the goose's movement
- The points are uploaded to a website -> KML
```{r}
ggmap(b) + 
  geom_point(data = snow, aes(Longitude, Latitude), color = "maroon", size = 1, alpha = 0.7) +
           labs(x = "Longitude", y = "Latitude", title = "Snow Goose '180965' Locations")+
  theme(plot.title = element_text(size = rel(1.25), hjust = 0.5))
```


```{r include=FALSE}
goose <- readr::read_csv("Data/Goose_data_2019.csv")
```

## Exploring Goose Measurement Dataset
```{r}
dim(goose)
```
```{r}
names(goose)
```

## Checking for NAs
- NAs in Dataset appeared to be correctly registered
```{r}
naniar::miss_var_summary(goose)
```

## Tidying Dataset: Part 1
- Replacing Spaces with Underscore, and # with "Number"
```{r echo=TRUE, message=FALSE, warning=FALSE}
names(goose)<-gsub("\\s","_",names(goose))#Put_in names
names(goose)<-gsub("#","Number",names(goose))
```
- Mutated Columns to be factors/numerics using mutate_at()


## Tidying Dataset: Part 2
- Renamed Columns to include measurements
  -Ex. rename(Wing_Chord_mm = Wing_Chord)
- Made Measurement a Variable
- pivot_longer(Wing_Chord_mm:Bill_Height_mm, <br>
               names_to = "Measure", <br>
               values_to = "Value")




